```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Introduction: What's the deal with native plants? {.unnumbered}

## Why should I bother switching to native plants and/or putting more effort into my yard?

-   Saving the world
-   Saving you money

### Saving the world

Several big problems can be addressed with native plants

-   The biodiversity crisis in general
    -   The insect apocalypse in particular
    -   Invasive species harming local ecosystems
-   Water shortages
-   Carbon footprints


#### Are you really serious, I don't think my garden can save the world.

Actually, it can! Every plant can make a difference in ever-expanding human colonization of the landscape [@vogtRewildingSuburbiaAmerican2023].

Water usage by lawns.

Carbon footprint of shipping non-native plants or cut flowers, foods.


#### I live in an apartment, I don't think so.
Container gardening info.

### Saving you money
- Water shortages
- Endless annuals from big box stores
- Fewer plants that fail dramatically
- Tax dollars spent keeping invasive species out of special places like public lands
- Tax subsidies spent keeping invasive species out of food/agricultural lands



## Book info

This document was created are using the **quarto** package [@R-quarto] to format this book. Some ideas from [@odellHowNothing2019].

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "quarto"
), 'packages.bib')
```
