--- 
title: "Cast Iron Garden: Plants for Scared People in Central Oklahoma"
author: "C.M. Curry and P.M. Cimprich"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: baeolophus/cast_iron_garden
description: "Plants for nervous gardeners."
---

```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Introduction and notes to self

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.
-Gardening for scared people.  Plants are easy and it's okay if some die.  That's how gardening works.
-Soil types in Norman area and pictures of them wet and dry and crumbliness
-Lawn post
-Tree post
-Easy ways to start
-Calendar of seasons and what to do when
-Which plants look dead in the winter but will come back
-Is the plant movable and when is best and how
-Species accounts with pictures of all stages and seeds

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
