```{r, include=FALSE}
options(tinytex.verbose = TRUE)
```

# Introduction: What's the deal with native plants? {.unnumbered}

## Why should I bother switching to native plants and/or putting more effort into my yard?

-   Saving the world
-   Saving you money

### Saving the world

Several big problems can be addressed with native plants

1. The biodiversity crisis in general
    a. The insect apocalypse in particular
    b.  Invasive species harming local ecosystems
2. Water shortages
3. Carbon footprints


#### Are you really serious, I don't think my garden can save the world.

Actually, it can! Every plant can make a difference in ever-expanding human colonization of the landscape [@vogtRewildingSuburbiaAmerican2023].  Many insects are tiny, and thus even tiny changes can help them [@TinyPlacesTiny].

Water usage by lawns.

Carbon footprint of shipping non-native plants or cut flowers, foods.


#### I live in an apartment, I don't think so.
Container gardening info.

### Saving you money
- Water shortages
- Endless annuals from big box stores
- Fewer plants that fail dramatically
- Tax dollars spent keeping invasive species out of special places like public lands
- Tax subsidies spent keeping invasive species out of food/agricultural lands



## Book info

This document was created are using the **quarto** package [@R-quarto] to format this book. Some ideas from [@odellHowNothing2019].

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), "quarto"
), 'packages.bib')
```
